Dear Université Laval Search Committee,
\vspace{1.0em}

\hspace{1.5em} I am writing to express my strong interest in the tenure-track Assistant Professor position in theoretical physics at the Département de physique, de génie physique et d'optique. As a PhD candidate in Complex Systems at Toronto Metropolitan University, expected to defend in 2026, I am particularly excited about the position's emphasis on complex systems and networks, which directly aligns with my doctoral research in computational modeling, statistical mechanics, and network dynamics. My interdisciplinary background bridges theoretical physics concepts with complex systems analysis, positioning me to contribute meaningfully to your department's research excellence and the January 1, 2026 start date aligns perfectly with my academic timeline.
\vspace{1.0em}

\hspace{1.5em} My research directly addresses the department's core areas in complex systems and networks, utilizing statistical mechanics, graph theory, and nonlinear dynamics to build mathematical models with applications in epidemiology, network science, and computational physics. My work on pandemic dynamics employs theoretical frameworks rooted in statistical mechanics and phase transitions, while my network analysis research draws from differential geometry and mathematical physics principles. This foundation positions me to contribute to theoretical high-energy physics collaborations, particularly in areas where complex systems approaches illuminate collective phenomena and emergent behaviors in quantum field theory and cosmological models. My publications demonstrate how complex systems methodologies can provide novel insights into fundamental physical processes.
\vspace{1.0em}

\hspace{1.5em} My commitment to interdisciplinary collaboration aligns perfectly with Université Laval's emphasis on partnerships with affiliated research centers including CRM, CRAQ, CIMM, and the Centre de recherche en données massives. I have successfully collaborated across computer science, mathematics, physics, and biology, developing expertise in communicating complex theoretical concepts across disciplinary boundaries. This experience prepares me to bridge complex systems approaches with theoretical physics research, potentially contributing to projects in mathematical physics, astroparticle physics, and cosmological modeling. My mentoring experience with undergraduate researchers has strengthened my commitment to supervising Master's and PhD students, fostering their development in both theoretical rigor and interdisciplinary thinking.
\vspace{1.0em}

\hspace{1.5em} I am particularly excited about establishing an independent research program that extends complex systems methodologies into theoretical physics domains, contributing to both the department's research excellence and its educational mission. My vision includes developing novel applications of statistical mechanics and network theory to problems in quantum field theory, potentially exploring phase transitions in gauge theories, complex network structures in cosmological models, and emergent phenomena in many-body quantum systems. I am committed to securing external funding from government agencies to support this research program and to teaching at undergraduate and graduate levels, bringing interdisciplinary perspectives to theoretical physics education while contributing meaningfully to departmental service and academic community building.
\vspace{1.0em}

\hspace{1.5em} Je suis particulièrement enthousiaste à l'idée de retrouver mes racines francophones et de contribuer à l'excellence académique dans un contexte francophone. Cette opportunité représente non seulement un retour vers mon héritage linguistique et culturel, mais également une chance de développer un programme de recherche innovant en physique théorique dans un environnement francophone dynamique. Je suis convaincu que cette immersion francophone enrichira ma perspective académique et renforcera ma capacité à communiquer des concepts complexes en physique théorique et systèmes complexes, contribuant ainsi de manière significative à la mission éducative et de recherche du département dans les deux langues officielles du Canada.
\vspace{1.0em}

\hspace{1.5em} Thank you for your consideration of my application. I would welcome the opportunity to discuss how my expertise in complex systems and statistical mechanics can contribute to the department's theoretical physics research areas, my vision for interdisciplinary collaborations with your affiliated research centers, and my commitment to excellence in research, teaching, and service. I am excited about the prospect of joining Université Laval's distinguished faculty and contributing to its mission of advancing knowledge in theoretical physics through rigorous scholarship and innovative pedagogy. Please find my curriculum vitae attached, which provides additional details about my research contributions and academic experience.
\vspace{1.0em}

Sincerely,\\
\myName\\[1.0em]
% \href{\myEmailHref}{%
%     \infobubblesm{\faAt}{cvblue}{iconcolour}{\myEmail}{}
% }\\[0.1em]
% \href{\myGitHubHref}{%
%     \infobubblesm{\faGithub}{cvblue}{iconcolour}{\myGitHub}{}
% }\\[0.1em]
% \href{\myLinkedInHref}{%
%     \infobubblesm{\faLinkedin}{cvblue}{iconcolour}{\myLinkedIn}{}
% }\\[0.1em]

