Dear Members of the Search Committee,
\vspace{1.0em}

\hspace{1.5em} I am writing to apply for the tenure-track faculty position in theoretical physics at Université Laval. As a PhD candidate in Complex Systems at Toronto Metropolitan University, my research bridges artificial intelligence, statistical physics, and network science, and I am eager to bring this expertise to Université Laval’s vibrant interdisciplinary environment.
\vspace{1.0em}

\hspace{1.5em} My doctoral work develops AI-driven approaches to fundamental problems in physics, with projects spanning adversarial reinforcement learning for network defense, cascading failure reduction in complex systems, and deep learning methods applied to nonlinear dynamics. This agenda aligns strongly with the department’s focus on both high-energy theory and complex systems. My publications and presentations—from modeling COVID-19 transmission with statistical physics to recent work on mitochondrial network dynamics—illustrate my ability to apply rigorous mathematical and computational methods across physics and interdisciplinary domains.
\vspace{1.0em}

\hspace{1.5em} In parallel with research, I have demonstrated a deep commitment to teaching and mentorship. As a Graduate Research Assistant, I have led undergraduate labs in data analysis and simulation, graded and supported coursework, and supervised thesis and summer research students. I view teaching not only as knowledge transfer but as an opportunity to cultivate curiosity and critical thinking. I am committed to delivering high-quality instruction in French, building on my fluency and experience working in bilingual academic settings.
\vspace{1.0em}

\hspace{1.5em} Collaboration has been central to my trajectory. I have worked closely with interdisciplinary teams spanning physics, epidemiology, and computer science, producing impactful publications and open-source tools. I am excited by the prospect of contributing to Université Laval’s strong network of research centers, particularly the CRM and IID, where my expertise in AI and network science can foster new connections and applications.
\vspace{1.0em}

\hspace{1.5em} I would be honored to join Université Laval’s faculty, advancing both independent and collaborative research, training the next generation of physicists, and contributing to the department’s academic community. I look forward to the opportunity to discuss how my background and vision can enrich your department’s research and teaching missions.
\vspace{1.0em}

Sincerely,\\
\myName\\[1.0em]
