Dear \company{} Hiring Team,
\vspace{1.0em}

\hspace{1.5em} I am writing to express my enthusiasm for the Machine Learning Engineer position at \company. With my current pursuit of a PhD in Complex Systems at Toronto Metropolitan University, set to complete in 2026, and a deep technical foundation in Python, PyTorch, TypeScript, and Julia, I am excited about the opportunity to contribute to your Applied AI and Machine Learning team.
\vspace{1.0em}

\hspace{1.5em} My academic and professional journey has been characterized by a keen interest in data-activated content generation and AI decisioning, making \company’s mission particularly resonate with my aspirations of building complex systems. I bring a proven track record in developing machine learning models that have significantly improved system performance, notably within AI-driven security enhancements and pandemic trend analytics projects. These experiences have equipped me with a solid understanding of machine learning fundamentals and a high level of proficiency in Python and PyTorch, aligning closely with the qualifications sought for this role.
\vspace{1.0em}

\hspace{1.5em} Collaborating with interdisciplinary teams, I have honed my ability to generate actionable insights into customer behavior, a skill that I am eager to apply in enhancing \company’s \product. My experience in feature creation and model deployment, complemented by a rigorous analytical approach nurtured through extensive research, positions me to contribute meaningfully to your team.
\vspace{1.0em}

\hspace{1.5em} I am particularly attracted to the collaborative culture at \company{} and the emphasis on continuous learning and improvement. The prospect of working end-to-end on large-scale machine learning systems, with the chance to impact millions of customers, excites me. I am keen to bring my background in computational modeling and data analysis to \company, where I can contribute to maximizing revenue, simplifying workflows, and boosting marketing agility for your global client base.
\vspace{1.0em}

\hspace{1.5em} Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and enthusiasms align with the needs of your team and to contribute to the innovative projects at \company. Please find my resume attached for more details on my accomplishments.
\vspace{1.0em}

Sincerely,\\
\myName\\[1.0em]
% \href{\myEmailHref}{%
%     \infobubblesm{\faAt}{cvblue}{iconcolour}{\myEmail}{}
% }\\[0.1em]
% \href{\myGitHubHref}{%
%     \infobubblesm{\faGithub}{cvblue}{iconcolour}{\myGitHub}{}
% }\\[0.1em]
% \href{\myLinkedInHref}{%
%     \infobubblesm{\faLinkedin}{cvblue}{iconcolour}{\myLinkedIn}{}
% }\\[0.1em]
